A Switching Planner for Combined Task and Observation Planning

### 2011-02-08 subarchitectures/planner.sa/trunk/src/latex/AAAI11/conc.tex
new conclusion

For use in an integrated continual planning and execution monitoring
system on a mobile robot platform, we developed a planner that
switches between fast sequential and expensive DT planning. Given a
DTPDDL model of the environment, sequential planning is used to
compute an initial deterministic sequential plan and complementary
runtime evolution of the decision process. That plan is executed until
testing of an assumption about the runtime state is scheduled. At that
point a DT session performs some sensing which determines whether or
not the sequential session should be allowed to continue, or otherwise
acts to achieve the overall objectives. We find our approach performs
quickly and relatively efficiently in a number of large real-world
task and observation planning problems.

>>>>

For use in an integrated continual planning and execution monitoring
system on a mobile robot platform, we developed a planner that
switches between: (a) fast sequential planning, and (b) expensive DT
planning in small abstractions of the problem at hand. Given a DTPDDL
model of the environment, sequential planning is used to compute an
initial sequential plan and complementary runtime evolution of the
decision process. That plan is executed until the outcome of the next
action scheduled for execution is too uncertain. At that point a DT
session performs sensing that can help determine how the sequential
plan might evolve, or otherwise acts to achieve the goals. We find our
approach performs quickly and relatively efficiently in a number of
large real-world task and observation planning problems.

### 2011-02-08 subarchitectures/planner.sa/trunk/src/latex/AAAI11/relatex.tex
new conclusion

Addressing task and observation planning specifically, there have been
a number of recent developments where the underlying problem is
modelled as a POMDP.
%%
For vision algorithm
selection,~\citeauthor{hippo-jnl}~(\citeyear{hippo-jnl}) exploit an
explicitly modelled hierarchical decomposition of the underlying
POMDP. \citeauthor{doshi08:pref_elic}~(\citeyear{doshi08:pref_elic})
represent a preference elicitation problem as a POMDP and take
advantage of symmetry in the belief-space to exponentially shrink the
state-space. Although we have been actively exploring
the \citeauthor{doshi08:pref_elic} approach, those exploitable
symmetries are not present in problems we consider due to the task
planning requirement.
%%
Finally, our approach is in a similar vein to {\em dual-mode}
control~\cite{cassandra96actingunder}, where planning switches between
entropy and utility focuses.

>>>>

Addressing task and observation planning specifically, there have been
a number of recent developments where the underlying problem is
modelled as a POMDP.
%%
For vision algorithm
selection,~\citeauthor{hippo-jnl}~(\citeyear{hippo-jnl}) exploit an
explicitly modelled hierarchical decomposition of the underlying
POMDP. \citeauthor{doshi08:pref_elic}~(\citeyear{doshi08:pref_elic})
represent a preference elicitation problem as a POMDP and take
advantage of symmetry in the belief-space to exponentially shrink the
state-space. Although we have been actively exploring
the \citeauthor{doshi08:pref_elic} approach, those exploitable
symmetries are not present in problems we consider due to the task
planning requirement.
%%
Also, our approach is in a similar vein to {\em dual-mode}
control~\cite{cassandra96actingunder}, where planning switches between
entropy and utility focuses.
